\pkg{depmixS4} : An \proglang{R}-package for Hidden Markov Models

### 2010-07-02 papers/jss/dpx4Rev.Rnw
updates to formating ...
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/depmix@429 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

<<echo=FALSE,results=hide>>=	
options(prompt="R> ", continue="+	",width=70, useFancyQuotes=FALSE,
digits=3)
library(depmixS4)
@

@@

The \code{fit} method is defined as follows: 
<<>>=
setMethod("fit","exgaus",
  function(object, w) {
    if(missing(w)) w <- NULL
    y <- object@y

	fit <- gamlss(y~1,weights=w,family=exGAUS(),
      control=gamlss.control(n.cyc=100,trace=FALSE),
      mu.start=object@parameters$mu, sigma.start=exp(object@parameters$sigma), 
      nu.start=exp(object@parameters$nu)
	)

@@

We first create all the response models that we need as a double list: 
<<>>=
rModels <- list()
rModels[[1]] <- list()
rModels[[1]][[1]] <- exgaus(speed$rt, pstart=c(5,.1,.1))
rModels[[1]][[2]] <- GLMresponse(formula=corr~1, data=speed, 
	family=multinomial(), pstart=c(0.5,0.5))

@@

Next, we define the transition and prior probability models using the 
\code{transInit} function (which produces a transInit model, which also extends 
the response class): 
<<>>=
trstart=c(0.9,0.1,0.1,0.9)
transition <- list()
transition[[1]] <- transInit(~Pacc,nst=2, data=speed, 
	pstart=c(0.9,0.1,0,0))
transition[[2]] <- transInit(~Pacc,nst=2, data=speed, 
	pstart=c(0.1,0.9,0,0))
inMod <- transInit(~1, ns=2, pstart=c(0.1,0.9), data=data.frame(1))
@

>>>>

<<echo=FALSE,results=hide>>=	
options(prompt="R> ", continue="+	",width=70, useFancyQuotes=FALSE,
digits=4)
library(depmixS4)
@

@@

The \code{fit} method is defined as follows: 
<<echo=FALSE>>=
options(width=60)
@
<<>>=
setMethod("fit","exgaus",
  function(object, w) {
    if(missing(w)) w <- NULL
    y <- object@y

	fit <- gamlss(y~1,weights=w,family=exGAUS(),
      control=gamlss.control(n.cyc=100,trace=FALSE),
      mu.start=object@parameters$mu, 
	  sigma.start=exp(object@parameters$sigma), 
      nu.start=exp(object@parameters$nu))

@@

We first create all the response models that we need as a double list: 
<<echo=FALSE>>=
options(width=80)
@
<<>>=
rModels <- list()
rModels[[1]] <- list()
rModels[[1]][[1]] <- exgaus(speed$rt, pstart=c(5,.1,.1))
rModels[[1]][[2]] <- GLMresponse(formula=corr~1, data=speed, 
	family=multinomial(), pstart=c(0.5,0.5))

@@

Next, we define the transition and prior probability models using the 
\code{transInit} function (which produces a transInit model, which also extends 
the response class): 
<<echo=FALSE>>=
options(width=70)
@
<<>>=
trstart=c(0.9,0.1,0.1,0.9)
transition <- list()
transition[[1]] <- transInit(~Pacc,nst=2, data=speed, 
	pstart=c(0.9,0.1,0,0))
transition[[2]] <- transInit(~Pacc,nst=2, data=speed, 
	pstart=c(0.1,0.9,0,0))
inMod <- transInit(~1, ns=2, pstart=c(0.1,0.9), data=data.frame(1))
@
